---
title: "Diamonds_exercises"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)

```

## The `diamonds` Dataset

Exercise 9.1 (Examine structure)
What type of data is contained in each column? Use some of the functions we introduced in the dataframes section to explore the basic structure of our new object.

```{r}
# Variable names
names(diamonds)

# A compact view
glimpse(diamonds)

# Summary statistics
summary(diamonds)
```

Our data:

```{r}
diamonds
```

# Exercises I

Exercise 9.2 (Counting individual groups)
How many diamonds with a clarity of category "IF" are present in the data-set?

```{r}
sum(diamonds$clarity == "IF")

diamonds %>% 
  group_by(clarity) %>% 
  count()

table(diamonds$clarity)

table(diamonds$clarity, diamonds$color)
```


Exercise 9.3 (Measuring proportions)
What fraction of the total do they represent?
Exercise 9.4 (Summarizing proportions)
What proportion of the whole is made up of each category of clarity?
Exercise 9.5 (Finding prices I)
What is the cheapest diamond price overall?
Exercise 9.6 (Finding prices I)
What is the range of diamond prices?
Exercise 9.7 (Finding prices II)
What is the average diamond price in each category of cut and color?
