---
title: "Diamonds_exercises"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
```

## The `diamonds` Dataset

Exercise 9.1 (Examine structure)

- What type of data is contained in each column?

- Use some of the functions we introduced in the dataframes section to explore the basic structure of our new object.

The dataset contains the following variables:

```{r ex9_1, echo=FALSE}
# Variable names
# names(diamonds)

# A compact view
glimpse(diamonds)

# Summary statistics
# summary(diamonds)
```

Our data:

```{r}
diamonds
```

## Exercise 9.2 (Counting individual groups)

How many diamonds with a clarity of category "IF" are present in the dataset?

```{r}
(num_IF <- sum(diamonds$clarity == "IF"))

diamonds %>% 
  group_by(clarity) %>% 
  count()

table(diamonds$clarity)

table(diamonds$clarity, diamonds$color)
```

A: From a total of `r nrow(diamonds)` diamonds, there are `r num_IF` IF clarity diamonds in our dataset.

## Exercise 9.3 (Measuring proportions)

- What proportion (0-1) (or percentage (0-100)) of the total do they represent?

```{r}
num_IF / nrow(diamonds) # proportion

num_IF / nrow(diamonds) * 100 # percent
```

## Exercise 9.4 (Summarizing proportions)

- What proportion of the whole is made up of each category of clarity?

```{r echo=FALSE}

diamonds %>%
  count(clarity) %>%
  mutate(
    # n_ = n(), # 8, n from input, not diamons
    # n_row = nrow(diamonds),
    prop = n/nrow(diamonds)) %>% 
  knitr::kable(caption = "The proportion of each type of clarity diamond.")


# Longer form:
diamonds %>% 
  group_by(clarity) %>% 
  summarise(n = n()/nrow(diamonds)) 
  
# The intersection of two variables (as a data.frame)
# with grouping by clarity
diamonds %>% 
  group_by(clarity, color) %>% 
  summarise(n = n())

# A contigency table (not a data.frame object)
table(diamonds$clarity, diamonds$color)

table(diamonds$clarity) / length(diamonds$clarity)
table(diamonds$clarity) / nrow(diamonds)

```

## Exercise 9.5 (Finding prices I)

- What is the cheapest diamond price overall?

```{r}
min(diamonds$price)
```

- What are the properties of the cheapest and the most expensive diamonds?

```{r}

```

## Exercise 9.6 (Finding prices I)

- What is the range (single number, Q4-Q0) of diamond prices?

```{r}

```

- The min & max, separately, for each category of cut and color? How would you summarize what the results? 

```{r}

```

- Produce a plot from the previous exercise. Does this change how you would summarize the previous result?

```{r}

```

## Exercise 9.7 (Finding prices II)

- What is the average diamond price in each category of cut and color?

```{r}

```

- Plot the raw values for each of the above groups _and_ the mean and standard deviation.

```{r}

```

- Are boxplots useful when representing this data?

```{r}

```

## Exercise 9.8 (Plotting)

- Produce a plot that shows the relationship between the size of a diamond (as measured by carat) and the price. 

```{r}

```

- Is a transformation of either axis in order? How would you apply it?

```{r}

```

- How can we distinguish between different groups of categorical variables, such as cut, clarity or color? 

```{r}

```

- How about other continuous variables? 

```{r}

```


